Molecular transport in human pial perivasculature

### 2024-11-18 paper/supplementary_main.tex
Updates in CSF flow model description
Former-commit-id: 423b4a85d4efc35597c4c1cb144d9047fdea5bbb [formerly 4f0e343c77b5e54c0f7fef108d821346b20faa9e]
Former-commit-id: 8ac31944effe4346db0c8a30d960464fda95b132

We supplement~\eqref{eq:3d_pde} and~\eqref{eq:interface:3d} with the following boundary conditions representing a given molecular influx at $\Gamma_{\rm SSAS}$, molecular efflux at a constant update rate $\beta_{\rm exit}$ at $\Gamma_{\rm AM-U}$, and no influx or efflux elsewhere from the CSF spaces.
\begin{alignat}{2}
(D \nabla (\phi c) - \bm u c ) \cdot \bm{n} &= g_{\mathrm{influx}} &&  \quad  \mathrm{on} \quad \Gamma_{\rm SSAS},  \\ 
% (-D \nabla (\phi c) + \bm u c ) \cdot \bm{n}_{\Gamma_{\rm SAS}} &= 0 &&  \quad  \mathrm{on} \quad \Gamma_{\rm SAS}^{\mathrm{out}}  \\ 
(-D \nabla (\phi c) + \bm u c ) \cdot \bm{n} & = \beta c  &&  \quad  \mathrm{on} \quad \Gamma_{\rm AM-U},  \\ 
(-D \nabla (\phi c) + \bm u c ) \cdot \bm{n} & = 0  &&  \quad  \mathrm{on} \quad \Gamma_{\rm AM-L} \discuss{\cup \Gamma_{\rm SC}}  .
\end{alignat} 
where again $\bm n$ denotes the outward-pointing boundary normal.

@@

\mer{MER: Stopped here.}

\subsubsection{Incompressible Stokes flow of CSF in the SAS and ventricular system}

We consider non-zero convection in the CSF space $u_{\rm CSF} \not = 0$ in \eqref{eq:multi_transport_3d} resulting from steady state CSF production.  Recall that $\Omega_{\mathrm{CSF}}$ represents the CSF space and that $\Gamma_{\mathrm{skull^{u/l}}}$ and $\Gamma_{\mathrm{pia}}$, $\Gamma_{\mathrm{LV}}$ represent the boundaries facing the upper and lower parts of the dura, the pia and the lateral ventricles, respectively.  Assuming CSF production in the choroid plexus located at the lateral ventricle wall, we solve the  steady state Stokes equations for the velocity and the pressure $(\bm u_{\mathrm{CSF}}, p_{\mathrm{CSF}})$ in the CSF domain: 
\begin{subequations}
    \begin{alignat}{2}
 - \mu \Delta \bm u_{\mathrm{CSF}} + \nabla p_{\rm{CSF}} & =  0 \quad && \mathrm{in} \,\,  \Omega_{\rm CSF}, \label{eq:momnetum_equation}  \\ 
 \nabla \cdot  \bm u_{\mathrm{CSF}} & = 0 \quad && \mathrm{in} \,\,   \Omega_{\rm CSF}, \label{eq:divergence_equation}  \\ 
\mu \nabla \bm u_{\mathrm{CSF}} \cdot \bm{n} -  p \bm n  &  = -R_0 ( \bm u \cdot \bm n ) \bm n\,\,   && \mathrm{on}  \label{eq:efflux_condition} \,\, \Gamma_{\mathrm{skull^u}}, \\ 
\bm u_{\mathrm{CSF}} & = 0 && \mathrm{on} \,\, \Gamma_{\rm{pia}} \cup \Gamma_{\mathrm{skull^l}} \Gamma_{\rm{SSAS}}  \\
\bm u_{\mathrm{CSF}} \cdot \bm n & = \frac{1}{ |\Gamma_{\rm LV}|}  u_{\rm in}, \quad \bm u \cdot \bm \tau = 0 \quad && \mathrm{on} \,\, \Gamma_{\rm{LV}} .  
\end{alignat}
\end{subequations}
Here, $\bm n$ denotes the unit outward normal to the boundary, $\mu$ is the CSF viscosity, and $\bm u_{\rm in}$ is the steady CSF flow across the lateral ventricle wall, see \Cref{tab:pvs:parameters}.
Condition \eqref{eq:efflux_condition} models an efflux site with positive resistance $R_0 \geq 0$. The Stokes system is solved with the finite element software $FEniCS$, stored and then subsequently read for all the relevant solute transport simulations. See Figure~\ref{fig:csf_flow_cardiac} for a streamline visualization of the obtained velocity profile and \Cref{sec:details_numerical_method} for details on the numerical algorithm employed.

We do not explicitly model convection within the brain parenchyma $\Omega_{\rm PAR}$, and thus set ${\bm u} = {\bm u}_{\rm PAR} = 0$ there.

\subsubsection{Perivascular fluid flow induced by pressure gradients}

The production of CSF in the choroid plexus generates a small, but consistent pressure gradient within the intracranial space. To compute the resulting CSF flow within the PVS, we solve 1D Darcy equations in the PVS network. The unknowns are the averaged PVS velocity, $u_{\rm pvs} = \langle u_{v,s} \rangle$, and the cross-section pressure $p_{\rm pvs} $ (assumed to be constant in each cross-section). The system is given by  \cite{daversin2022geometrically, gjerde2024directional} 
\begin{alignat}{2}
A \,  u_{\rm pvs}   + \frac{\kappa}{\mu} \, A \, \partial_{s} p_{\rm pvs} & = 0, &&  \quad \rm in  \,\, \Lambda  \\ 
-\partial_s (A \, u_{\rm pvs}) & = f, && \quad \rm in  \,\, \Lambda .  
\end{alignat} 
In the above, $A$ is the area of the PVS, $\mu$ is the dynamic viscosity, and $\kappa$ is derived from the assumption of Poiseuille
flow in the annular cross-section of the PVS \cite{daversin2022geometrically,tithof2022network}: 
\begin{equation}
\kappa = \frac18 \left( R_2^2 + R_1^2 - \frac{1}{\ln(R_2/R_1)} (R_2^2- R_1^2) \right). 
\end{equation}
On bifurcations, conservation of fluxes is enforced weakly and continuity of the pressure is enforced strongly (in the choice of the finite element spaces).

@@

\subsection{Numerical Method}
\label{sec:details_numerical_method}
Here we provide details on the numerical method used to solve the coupled system. We are given a mesh $\mathcal{T}_h $, consisting of elements denoted by $E$, of $\Omega= \Omega_{\rm PAR} \cup \Omega_{\rm CSF}$.  The collection of all interior facets to $\Omega_{\rm PAR}$ (resp.  to $\Omega_{\mathrm{CSF}}$) is  denoted by $\mathcal{F}_{h,b}$ (resp. $\mathcal{F}_{h,c}$).  The union of all interior facets $\mathcal{F}_i = \mathcal{F}_{h,b} \cup \mathcal{F}_{h,c}$. Facets lying on the pial interface are denoted by $\mathcal{F}_{\Gamma_{\rm pia}}$, on the skull by $\mathcal{F}_{\Gamma_{\rm skull}}$, and on the spinal canal by $\mathcal{F}_{\Gamma_{\rm SAS}}$. Note that $\mathcal{F}_i \cap \mathcal{F}_{\Gamma_{\rm pia}} = \emptyset $. The union of all the facets is denoted by $\mathcal{F}_h$. The restriction of $\mathcal{T}_h $ to $\Omega_{\mathrm{CSF}}$ is denoted by $\mathcal{E}_{h}$. 
\subsubsection{CSF Flow}
We recall the system of equations that we approximate. Find $(\bm u, p)$ such that 
\begin{subequations}
    \begin{alignat}{2}
 - \mu \Delta \bm u + \nabla p & =  \bm 0 \quad && \mathrm{in} \,\,  \Omega_{\rm CSF}, \label{eq:momnetum_equation}  \\ 
 \nabla \cdot  \bm u & = 0 \quad && \mathrm{in} \,\,   \Omega_{\rm CSF}, \label{eq:divergence_equation}  \\ 
\mu \nabla \bm u \cdot \bm{n} -  p \bm n  &  = -R_0 ( \bm u \cdot \bm n ) \bm n, \,\,  \quad \bm u \cdot \bm \tau = 0 \quad  && \mathrm{on}  \label{eq:efflux_condition} \,\, \Gamma_{\mathrm{skull^u}}, \\ 
\bm u & = 0 && \mathrm{on} \,\, \Gamma_{\rm{pia}} \cup \Gamma_{\mathrm{skull^l}} \cup \Gamma_{\rm{SSAS}} \\
\bm u \cdot  \bm n   =  \frac{1}{|\Gamma_{\mathrm{LV}}|} u_{\mathrm{in}}  , & \; \; \bm u \cdot \bm \tau  = 0  && \mathrm{on} \;  \Gamma_{\mathrm{LV}},
\end{alignat}
\end{subequations}
We follow \cite{hong2016robust} and approximate the velocity field $u$ and the pressure $p$ with the following finite element spaces. 
\begin{align}
\bm V_h  & = \{ \bm v  \in H(\mathrm{div}; \Omega_{\mathrm{CSF}}): \; \bm v \vert_{E} \in \mathbb{BDM}^2 (E),  \; E \in \mathcal{E}_h; \;  \bm v \cdot \bm n = 0 \text{ on } \Gamma_{\rm{pia}} \cup \Gamma_{\mathrm{skull^l}} \cup \Gamma_{\rm{SSAS}}, \;\; \bm v \cdot \bm n = \frac{1}{|\Gamma_{\mathrm{LV}}|} u_{\mathrm{in}} \text{ on } \Gamma_{\mathrm{LV}} \} \\ 
S_h  & = \{q \in L^2(\Omega):  \;  q \vert_E \in \mathbb{P}^1(E),  \; E \in \mathcal{E}_h \}. 
\end{align}
Here, $H(\mathrm{div};\Omega)$ is the space of $L^2$ vector fields with $L^2$ divergence,  $\mathbb{BDM}^2$ is the Brezzi-Douglas--Marini element \cite{brezzi1987mixed} of order 2, and  $\bm n$ (resp. $\bm \tau$) is the unit outward normal (resp. tangent) vector.  
Given any vector $\bm v$, the normal and tangential components on each facet  are denoted by 
\[ 
\bm v_n = (\bm v \cdot \bm n)\bm n , \quad \bm v_t = (\bm v - \bm v_n). 
\]
Since $V_h \subset H(\mathrm{div}, \Omega_{\rm{CSF}})$, then $[\bm v_n] = 0 $ on $\mathcal{F}_{h,c}$. Continuity in the tangential component is enforced weakly via interior penalization. For notational simplicity, denote by $\mathcal{F}_{\Gamma}$ the facets lying on $\Gamma_{\rm{pia}} \cup \Gamma_{\mathrm{skull}} \cup \Gamma_{\rm{SSAS}} \cup \Gamma_{\mathrm{LV}}$. Define the form 
\begin{multline}
\mathcal{A}_h (\bm u, \bm v) = \sum_{E \in \mathcal{E}_h} \int_{E} \mu \nabla u : \nabla v - \sum_{
F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma} 
} \int_{F} \mu \{\nabla u\}\cdot \bm n_F \cdot [\bm v_t] 
\\ - \sum_{
F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma} 
} \int_{F} \mu \{\nabla v\}\cdot \bm n_F \cdot [\bm u_t]
+ \sum_{
F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma} 
} \frac{\sigma \mu}{h} \int_{F} [\bm u_t ] \cdot [\bm v_t].   
\end{multline}
We set $\sigma =20$. The discretization for the CSF flow, is then to find $(\bm u_h, p_h) \in \bm V_h \times S_h$ such  that 
\begin{align}
\mathcal{A}_h(u_h, v_h)  + \sum_{F \in \mathcal{F}_{\Gamma_{\mathrm{skull}}}} \int_{F} R_0 (\bm u_h \cdot \bm n) (\bm v_h \cdot \bm n) - \int_{\Omega} \nabla \cdot \bm v_h \, p_h  & = 0, \quad \forall \bm v_h \in \bm V_h   \\ 
(\nabla \cdot \bm u_h , q_h ) & = 0, \quad \forall q_h \in S_h.
\end{align}
\subsubsection{PVS flow}

@@

\subsection{Cardiac Dispersion Factor Estimation}

\subsubsection*{Dispersion in the CSF spaces}

@@

\subsubsection{Cardiac Dispersion Factor Estimation}\label{sec:dispersion_details}

>>>>

We supplement~\eqref{eq:3d_pde} and~\eqref{eq:interface:3d} with the following boundary conditions representing a given molecular influx at $\Gamma_{\rm SSAS}$, molecular efflux at a constant update rate $\beta_{\rm exit}$ at $\Gamma_{\rm AM-U}$, and no influx or efflux elsewhere from the CSF spaces.
\begin{subequations}
\begin{alignat}{2}
(D \nabla (\phi c) - \bm u c ) \cdot \bm{n} &= g_{\mathrm{influx}} &&  \quad  \mathrm{on} \quad \Gamma_{\rm SSAS},  \\ 
% (-D \nabla (\phi c) + \bm u c ) \cdot \bm{n}_{\Gamma_{\rm SAS}} &= 0 &&  \quad  \mathrm{on} \quad \Gamma_{\rm SAS}^{\mathrm{out}}  \\ 
(-D \nabla (\phi c) + \bm u c ) \cdot \bm{n} & = \beta c  &&  \quad  \mathrm{on} \quad \Gamma_{\rm AM-U},  \\ 
(-D \nabla (\phi c) + \bm u c ) \cdot \bm{n} & = 0  &&  \quad  \mathrm{on} \quad \Gamma_{\rm AM-L} \cup \Gamma_{\rm SC}  .
\end{alignat} 
\end{subequations}
where again $\bm n$ denotes the outward-pointing boundary normal.

@@

\subsubsection{Modelling CSF flow via the incompressible Stokes equations}

The time-independent, incompressible Stokes equations model the flow
of an incompressible Newtonian fluid at low Reynolds numbers, and read
as follows: over the domain $\Omega_{\rm CSF} \subset \R^3$, find the
velocity vector field $\bm u : \Omega_{\rm CSF} \rightarrow \R^3$ and
the pressure $p : \Omega_{\rm CSF} \rightarrow \R$ such that
\begin{subequations}
  \begin{alignat}{2}
    - \mu \Delta \bm u  + \nabla p &=  0 \quad && \text{ in } \Omega_{\rm CSF},
    \label{eq:momnetum_equation} \\ 
    \nabla \cdot \bm u &= 0 \quad && \text{ in } \Omega_{\rm CSF},
    \label{eq:divergence_equation} .
  \end{alignat}
\end{subequations}
In addition, we impose the following boundary conditions to model flow
induced by CSF production in the choroid plexus with $\Gamma_{\rm AM-U}$ as the main efflux site:
\begin{subequations}
  \begin{alignat}{2}
    \mu \nabla \bm u \cdot \bm{n} - p \bm n &= -R_0 ( \bm u \cdot \bm n ) \bm n
    && \text{ on } \Gamma_{\mathrm{AM-U}}, \\
    \bm u &= 0 && \text{ on } \Gamma_{\mathrm{AM-L}}, \\
    \bm u &= 0 && \text{ on } \Gamma_{\rm{pia}}, \\
    \bm u &= 0 && \text{ on } \Gamma_{\rm{SSAS}}, \\
    \bm u \cdot \bm n & = \frac{1}{ |\Gamma_{\rm LV}|}  u_{\rm in}, \quad \bm u \cdot \bm \tau = 0 \quad && \text{ on } \Gamma_{\rm{LV}} ,  
  \end{alignat}
\end{subequations}
where $\bm n$ denotes the unit outward normal to the boundary, $\mu$ is the CSF viscosity, $R_0 > 0$ is a resistance parameter for CSF efflux, and $u_{\rm in}$ is a given fluid influx, here across the lateral ventricle wall $\Gamma_{\rm LV}$. We consider alternative variations of these boundary conditions in connection with estimating dispersion effects induced by CSF pulsatility, see~\Cref{sec:supp:dispersion}.

%% We consider non-zero convection in the CSF space $u_{\rm CSF} \not = 0$ in \eqref{eq:multi_transport_3d} resulting from steady state CSF production.  Recall that $\Omega_{\mathrm{CSF}}$ represents the CSF space and that $\Gamma_{\mathrm{skull^{u/l}}}$ and $\Gamma_{\mathrm{pia}}$, $\Gamma_{\mathrm{LV}}$ represent the boundaries facing the upper and lower parts of the dura, the pia and the lateral ventricles, respectively.  Assuming CSF production in the choroid plexus located at the lateral ventricle wall, we solve the  steady state Stokes equations for the velocity and the pressure $(\bm u_{\mathrm{CSF}}, p_{\mathrm{CSF}})$ in the CSF domain:

\subsubsection{Flow in perivascular networks induced by pressure gradients}

To model flow induced by pressure differences between end nodes in a
perivascular network $\Lambda$, with segments $\Lambda^i$, internal
nodes $\mathcal{B}$ and end nodes $\mathcal{T}$, we consider the
following system of hydraulic network
equations~\cite{daversin2022geometrically, gjerde2024directional}. The
unknowns are the PVS velocity $u_{\rm pvs}$ and pressure $p_{\rm
  pvs}$, which represent the fluid velocity in the axial direction
averaged across the PVS cross-sections and the cross-section-average
fluid pressure, respectively, solving
\mer{MER: Stopped here.}
\begin{alignat}{2}
A \,  u_{\rm pvs}   + \frac{\kappa}{\mu} \, A \, \partial_{s} p_{\rm pvs} & = 0, &&  \quad \rm in  \,\, \Lambda  \\ 
-\partial_s (A \, u_{\rm pvs}) & = f, && \quad \rm in  \,\, \Lambda .  
\end{alignat} 
In the above, $A$ is the area of the PVS, $\mu$ is the dynamic viscosity, and $\kappa$ is derived from the assumption of Poiseuille
flow in the annular cross-section of the PVS \cite{daversin2022geometrically,tithof2022network}: 
\begin{equation}
\kappa = \frac18 \left( R_2^2 + R_1^2 - \frac{1}{\ln(R_2/R_1)} (R_2^2- R_1^2) \right). 
\end{equation}
On bifurcations, conservation of fluxes is enforced weakly and continuity of the pressure is enforced strongly (in the choice of the finite element spaces).

@@

\subsection{Numerical Method}
\label{sec:details_numerical_method}
Here we provide details on the numerical method used to solve the coupled system. We are given a mesh $\mathcal{T}_h $, consisting of elements denoted by $E$, of $\Omega= \Omega_{\rm PAR} \cup \Omega_{\rm CSF}$.  The collection of all interior facets to $\Omega_{\rm PAR}$ (resp.  to $\Omega_{\mathrm{CSF}}$) is  denoted by $\mathcal{F}_{h,b}$ (resp. $\mathcal{F}_{h,c}$).  The union of all interior facets $\mathcal{F}_i = \mathcal{F}_{h,b} \cup \mathcal{F}_{h,c}$. Facets lying on the pial interface are denoted by $\mathcal{F}_{\Gamma_{\rm pia}}$, on the skull by $\mathcal{F}_{\Gamma_{\rm skull}}$, and on the spinal canal by $\mathcal{F}_{\Gamma_{\rm SAS}}$. Note that $\mathcal{F}_i \cap \mathcal{F}_{\Gamma_{\rm pia}} = \emptyset $. The union of all the facets is denoted by $\mathcal{F}_h$. The restriction of $\mathcal{T}_h $ to $\Omega_{\mathrm{CSF}}$ is denoted by $\mathcal{E}_{h}$.

\subsubsection{CSF Flow}
%% We recall the system of equations that we approximate. Find $(\bm u, p)$ such that 
%% \begin{subequations}
%%     \begin{alignat}{2}
%%  - \mu \Delta \bm u + \nabla p & =  \bm 0 \quad && \mathrm{in} \,\,  \Omega_{\rm CSF}, \label{eq:momnetum_equation}  \\ 
%%  \nabla \cdot  \bm u & = 0 \quad && \mathrm{in} \,\,   \Omega_{\rm CSF}, \label{eq:divergence_equation}  \\ 
%% \mu \nabla \bm u \cdot \bm{n} -  p \bm n  &  = -R_0 ( \bm u \cdot \bm n ) \bm n, \,\,  \quad \bm u \cdot \bm \tau = 0 \quad  && \mathrm{on}  \label{eq:efflux_condition} \,\, \Gamma_{\mathrm{skull^u}}, \\ 
%% \bm u & = 0 && \mathrm{on} \,\, \Gamma_{\rm{pia}} \cup \Gamma_{\mathrm{skull^l}} \cup \Gamma_{\rm{SSAS}} \\
%% \bm u \cdot  \bm n   =  \frac{1}{|\Gamma_{\mathrm{LV}}|} u_{\mathrm{in}}  , & \; \; \bm u \cdot \bm \tau  = 0  && \mathrm{on} \;  \Gamma_{\mathrm{LV}},
%% \end{alignat}
%% \end{subequations}

We follow \cite{hong2016robust} and approximate the velocity field $u$ and the pressure $p$ with the following finite element spaces. 
\begin{align}
\bm V_h  & = \{ \bm v  \in H(\mathrm{div}; \Omega_{\mathrm{CSF}}): \; \bm v \vert_{E} \in \mathbb{BDM}^2 (E),  \; E \in \mathcal{E}_h; \;  \bm v \cdot \bm n = 0 \text{ on } \Gamma_{\rm{pia}} \cup \Gamma_{\mathrm{skull^l}} \cup \Gamma_{\rm{SSAS}}, \;\; \bm v \cdot \bm n = \frac{1}{|\Gamma_{\mathrm{LV}}|} u_{\mathrm{in}} \text{ on } \Gamma_{\mathrm{LV}} \} \\ 
S_h  & = \{q \in L^2(\Omega):  \;  q \vert_E \in \mathbb{P}^1(E),  \; E \in \mathcal{E}_h \}. 
\end{align}
Here, $H(\mathrm{div};\Omega)$ is the space of $L^2$ vector fields with $L^2$ divergence,  $\mathbb{BDM}^2$ is the Brezzi-Douglas--Marini element \cite{brezzi1987mixed} of order 2, and  $\bm n$ (resp. $\bm \tau$) is the unit outward normal (resp. tangent) vector.  
Given any vector $\bm v$, the normal and tangential components on each facet  are denoted by 
\[ 
\bm v_n = (\bm v \cdot \bm n)\bm n , \quad \bm v_t = (\bm v - \bm v_n). 
\]
Since $V_h \subset H(\mathrm{div}, \Omega_{\rm{CSF}})$, then $[\bm v_n] = 0 $ on $\mathcal{F}_{h,c}$. Continuity in the tangential component is enforced weakly via interior penalization. For notational simplicity, denote by $\mathcal{F}_{\Gamma}$ the facets lying on $\Gamma_{\rm{pia}} \cup \Gamma_{\mathrm{skull}} \cup \Gamma_{\rm{SSAS}} \cup \Gamma_{\mathrm{LV}}$. Define the form 
\begin{multline}
\mathcal{A}_h (\bm u, \bm v) = \sum_{E \in \mathcal{E}_h} \int_{E} \mu \nabla u : \nabla v - \sum_{
F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma} 
} \int_{F} \mu \{\nabla u\}\cdot \bm n_F \cdot [\bm v_t] 
\\ - \sum_{
F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma} 
} \int_{F} \mu \{\nabla v\}\cdot \bm n_F \cdot [\bm u_t]
+ \sum_{
F \in \mathcal{F}_{h,c} \cup \mathcal{F}_{\Gamma} 
} \frac{\sigma \mu}{h} \int_{F} [\bm u_t ] \cdot [\bm v_t].   
\end{multline}
We set $\sigma =20$. The discretization for the CSF flow, is then to find $(\bm u_h, p_h) \in \bm V_h \times S_h$ such  that 
\begin{align}
\mathcal{A}_h(u_h, v_h)  + \sum_{F \in \mathcal{F}_{\Gamma_{\mathrm{skull}}}} \int_{F} R_0 (\bm u_h \cdot \bm n) (\bm v_h \cdot \bm n) - \int_{\Omega} \nabla \cdot \bm v_h \, p_h  & = 0, \quad \forall \bm v_h \in \bm V_h   \\ 
(\nabla \cdot \bm u_h , q_h ) & = 0, \quad \forall q_h \in S_h.
\end{align}
\subsubsection{PVS flow}

@@

\subsection{Dispersion in the CSF spaces}
\label{sec:supp:dispersion}

@@

%\subsubsection{Cardiac Dispersion Factor Estimation}
%\label{sec:dispersion_details}
